Using reference models in variable selection \vspace{.1in}

### 2022-02-14 reviews/rebuttal.tex

\begin{reply}
Thank you for this comment. We have added some clarifications at the end of Section 2.2 with regard to building the reference model, where we write

\vspace{0.5\baselineskip}
\textit{
Clearly, the reference model approach requires a sensible reference model. The construction of such a model should follow proper modelling workflow \citep[see, e.g.][]{gelman2020bayesian}. Better predictive models imply better selection results. The goodness of a reference model comes from its predictive ability which should be assessed via proper validation methods. [...] In general, there is no restriction on the type of model the reference models should be and a sensible reference model does not even need to be Bayesian necessarily.
}
\vspace{0.5\baselineskip}

As such, for example, a model predicting constant output or a model predicting uncorrelated noise are not useful reference models.

The sensitivity of the Bayesian models to choice of priors is well studied and there exists well-developed workflows for doing prior sensitivity analysis and other model checking \citep[see, e.g.][]{gelman2020bayesian}. As such, the aim of this paper is not to show how to build good reference models. Instead, we study the importance of reference models in submodel inference using either the decision theoretically justified version or other algorithms that we show can also be improved by replacing the data with filtered prediction from the reference model.

The reference models applied in the examples are using widely accepted weakly informative priors and there are no prior sensitivity issues for them. As the same reference models are used for all algorithms, the relative comparison between different algorithms and the overall usefulness of the reference model approach is not influenced by the details of the reference models.
\end{reply}

@@

\begin{point}
Section 4.1, page 8, line 38: $\text{elpd}_\text{base}$ should be $\text{elpd}_\text{best}$
\end{point}

\begin{reply}
Thanks for pointing out the typo. We have fixed it.
\end{reply}

\begin{point}
How is calculated the probability used in the stopping rule (2)? Using the reference model?
\end{point}

\begin{reply}\label{reply:stopping}
At each iteration, the best model is selected via the default stopping rule implemented in the \texttt{R}-package \texttt{projpred}. For details, see \citet{paper:projpred}. The predictive performance is evaluated via cross-validation both for the reference model and the submodels using the expected log-predictive density (elpd) score. The obtained elpd samples form a distribution than can be used to estimate said probability. We have added following sentence:
TODO: is the sentence below enough? Paul: Please note my change to the below sentence.
\end{reply}

\textit{
\ldots and the probability is computed from a normal approximation of the uncertainty in the cross-validation performance comparison using the mean and standard error of the elpd difference between reference and submodel \citep{Vehtari+etal:2017:practical,paper:projpred,Sivula+etal:2020:loo_uncertainty}.
}

@@

\begin{point}
It is not very exigent in (2) to impose that $\text{elpd}_i-\text{elpd}_\text{best}>0$? Perhaps you should consider other limits similar to those used in Bayes factors (Kass and Raftery, 1995) and not to choose only on solution but to explore other possible solutions in the spirit of Occam’s window
\end{point}

\begin{reply}
The above condition is derived from the original criteria to choose the model size in \citet{paper:projpred} for the use of the projection predictive approach in the minimal subset scenario. In that case, the comparison is between the predictive score of the submodel of size $i$ and the reference model. Here we decided to compare the submodel of size $i$ with the ``best'' size, at the given iteration, due to the natural loss of explanatory power of the remaining covariates as the iterations increase. \\
In general, the condition is expressed as the probability of that event, which is anyhow less exigent than the inequality itself. We don't want to imply that this procedure could not be improved somehow to take, for example, something like Occam's window into account. However, since the projection predictive approach was not the main point of this paper, we cannot reasonably address it here and leave it for future research. We have added a following sentence to the paper.
TODO: would this be enough? Paul: please note that I changed the sentence below
\end{reply}

\vspace{0.5\baselineskip}
\textit{
We have used the stopping rule recommended by \citet{paper:projpred} for the minimal subset selection, but other stopping rules would be possible in the iterative case and may be worth further research.
}

@@

	\vspace{0.5\baselineskip}

\end{reply}

\begin{point}
Please include the computational cost of compared approaches in Section 2.1. 
\end{point}

\begin{reply}
Thanks for the suggestion. We discuss the computational aspects in Section 2.2. In general, the reference model approach has the additional cost of fitting the reference model before performing selection. However, this reference models is usually available anyway when building up a model via robust workflows \citep{gelman2020bayesian}. Therefore, in these cases there is no additional cost. In any case we believe that the benefits of a more stable and efficient selection overcome the cost of fitting a reference model.
\fede{We added a new table (Table 3) reporting the computational time for the bodyf fat example, showing how the burden is divided between the fit of the reference model and the rest of the selection procedure.}
Paul: why is this still in red?
\end{reply}

### 2022-02-16 reviews/rebuttal.tex

% This refines the format of how the reviewer/point reference will appear.
\renewcommand{\thepoint}{P\,\thereviewer.\arabic{point}}

% command declarations for reviewer points and our responses
\newcommand{\reviewersection}{\stepcounter{reviewer} \bigskip \hrule
                  \section*{Reviewer \thereviewer}}

\newenvironment{point}
   {\refstepcounter{point} \bigskip \noindent \begin{sf}{\textbf{Reviewer~Point~\thepoint} } ---\ }
   {\par \end{sf}}

 \newcommand{\shortpoint}[1]{\refstepcounter{point}  \bigskip \noindent
   \begin{sf}
     {\textbf{Reviewer~Point~\thepoint} } ---~#1\par
   \end{sf}}

@@

\begin{aecomment}
Please note the strong concerns of the reviewers. If you cannot implement a better projective prediction approach for complete variable selection problems, then at the very least, I would expect you to motivate why it's worth knowing about this approach; you show that it doesn't work very well.
\end{aecomment}

\begin{reply}
Based on the reviewers' comments and suggestions, we have substantially improved our paper. In particular, we hope that we now better explain the purpose of our work, which was a source of confusion in our original version.

We hope that this specifically clarifies one misunderstanding on the purpose of our work highlighted by Reviewer 1 as we now better explain that the projective prediction approach for complete variable selection is not the main aim of the paper. This method has been included solely for the sake of a more exhaustive comparison, because of the good performances of the projective prediction method (projpred) for minimal variable selection. Indeed, we have highlighted how projpred has been designed specifically for the minimal selection case, making it non-trivial to extend for the complete selection. We cannot rule out that better projective prediction methods for complete selection can be designed in the future but this is not in the scope of this paper.

Reviewer 3 gave precious comments on how to clarify the real intentions of our work, which is the study of the effect of reference models when used to guide the selection process, regardless of the selection method. We followed the suggestions, and we believe that the current version reduces the possibility of misunderstandings.
\end{reply}

@@

		Moreover, we clarified that the projective prediction approach for complete variable selection is not the main aim of this work. The method has been included solely for the sake of a more exhaustive comparison, since the good performances of the projective prediction method (projpred) for minimal variable selection. Indeed, we have highlighted how projpred has been designed specifically for the minimal selection case, making it non-trivial to extend for the complete selection. We cannot rule out that better projective prediction methods for complete selection can be designed in the future but this is not in the scope of this paper. 
\end{reply}

% Point one description 
\begin{point}
My main concern with respect to the projective predictive approach is the robustness of the results to the reference model. Apparently, you can build very different references models to the same data set: have you study the sensitivity of the results with different reference models?. You use Bayesian models as reference models and, in these cases, the determination of prior distribution is not very clear. You can build hundreds and hundreds of prior distribution: for instance in (7) you can have use standard inverted gamma priors on $\tau^2$ and $\sigma^2$ by determining the parameters of the prior in order to the prior mixture gives reasonable results about the data using the prior mixture. How can you study the robustness of your results to this important aspect?
\end{point}

\begin{reply}
Thank you for this comment. We have added some clarifications at the end of Section 2.2 with regard to building the reference model, where we write

\vspace{0.5\baselineskip}
\textit{
Clearly, the reference model approach requires a sensible reference model. The construction of such a model should follow proper modelling workflow \citep[see, e.g.][]{gelman2020bayesian}. Better predictive models imply better selection results. The goodness of a reference model comes from its predictive ability which should be assessed via proper validation methods. [...] In general, there is no restriction on the type of model the reference models should be, and a sensible reference model does not even need to be Bayesian necessarily.
}
\vspace{0.5\baselineskip}

@@

As such, for example, a model predicting constant output or a model predicting uncorrelated noise are not useful reference models.

The sensitivity of the Bayesian models to choice of priors is well studied, and there exists well-developed workflows for doing prior sensitivity analysis and other model checking \citep[see, e.g.][]{gelman2020bayesian}. As such, the aim of this paper is not to show how to build good reference models. Instead, we study the importance of reference models in submodel inference using either the decision theoretically justified version or other algorithms that we show can also be improved by replacing the data with filtered prediction from the reference model.

The reference models applied in the examples are using widely accepted weakly informative priors, and there are no prior sensitivity issues for them. As the same reference models are used for all algorithms, the relative comparison between different algorithms and the overall usefulness of the reference model approach is not influenced by the details of the reference models.
\end{reply}

@@

%\todo
%\begin{description}
%    \item[Mans] Clarified that we present first time how this problem should be approached in the Bayesian context.
%\end{description}

\begin{point}
Perhaps a solution to the previous problem would be to determine the reference model using frequentist MLE procedures that avoid the construction of prior distributions and use a single point prediction or, alternatively, to use the sampling distribution of MLE as a posterior distribution and take this “Bayesian” model as reference model. Do you have any experience in this line?
\end{point}

\begin{reply}
This is an interesting question. The way we see it is that MLE tends to be more unstable than comparable Bayesian approaches, as the latter get improved stability both from integration over the parameter space (instead of using only a point estimate), and can further be improved by using even just weakly informative priors (rather than improper flat priors). We have added references that discuss the merits of Bayesian approaches compared to MLE. Although we think Bayesian reference models are a better choice in most cases, we also assume that in large $n$, small $p$ cases there will be not much difference to using MLE to construct the reference model, and we believe that in what ever way the reference model has been built, if it's a good predictive model, it will be a useful reference model too.

@@

\vspace{0.5\baselineskip}

\textit{Such nature of the minimal subset makes the solution
	not unique, except in the particular case of completely orthogonal predictors. 
	The non-uniqueness of the solution is not a problem per se, as different samples of the data
	are expected to give possible different minimal subsets but with same predictive power. 
	However, it makes it difficult to define a proper
	concept of stability of the selection.}
\end{reply}

\begin{point}
In most of real situations, we have an M-open problem (particularly in big data problems) where the true generator mechanism is too complex and it is not included in the family of considered models. What would be the performance of your methodology if the reference model is far from the true generator process? How can you detect these situations?
\end{point}

\begin{reply}
We assume that all models are wrong. Analysing model misspecification is well studied in the Bayesian literature, and there are plenty of methods available for model checking \citep[see, e.g.][]{gelman2020bayesian}. The reference model approach assumes we have first made the best possible model, following all the best practices for Bayesian model building \citep{gelman2020bayesian}. Even a misspecified model that would introduce some bias can reduce the variance so that the variable selection is improved via an improved bias-variance tradeoff. As the selection is to find a submodel that is not far from the reference model, the performance of the selected model is not far from the reference model.

@@

\begin{point}
Section 3.1: you say that in this simulation you use a Bayesian stepwise forward selection procedure. Is this really the case? In your description of the procedure in page
6 you exclude (and not include variables) in this step of the algorithm. In my view, this procedure is a Bayesian stepwise backward selection procedure.
\end{point}

\begin{reply}
Thanks for pointing out the typo. We fixed it in the new version of the paper.
\end{reply}

\begin{point}
In the Bayesian stepwise selection procedures of section 3.1 you use posterior pvalues to exclude variables, and you exclude the variable with the highest Bayesian p- value. Shouldn't you take into account whether the value of the pvalue is large or small? Shouldn't you calibrate these pvalues?
\end{point}

\begin{reply}
There is no need of calibrating these $p$-values, since they are used only to pre-select predictors for potential exclusion. Such a predictor is then excluded or not, by comparing the predictive performance of the reduced model without this predictor and the not-reduced model including the predictor. In such a way, the posterior $p$-values matter only in terms of their ordering, and not in terms of their magnitude.
\end{reply}

@@

\begin{point}
Section 3.1 steplm procedure: Why have you chosen the AIC criterion which, as it is well-known tend to select non-parsimonious models? Have you tried to use the BIC criterion instead? In my experience, this criterion tend to select more parsimonious models and in a M Complete approach, it is usually consistent.
\end{point}

\begin{reply}
We used AIC because \citet{heinze2018variable} used AIC in the steplm procedure, and we wanted our results to be comparable to their results. The goal of our paper was not to compare all possible information criteria but to investigate whether using reference models helps variable selection methods. We made some choices to keep the paper within reasonable length and complexity. Based on the results, we assume that variable selection using any *IC approach will benefit from using a reference model. 
\end{reply}

@@

\begin{reply}\label{reply:stopping}
At each iteration, the best model is selected via the default stopping rule implemented in the \texttt{R}-package \texttt{projpred}. For details, see \citet{paper:projpred}. The predictive performance is evaluated via cross-validation both for the reference model and the submodels using the expected log-predictive density (elpd) score. The obtained elpd samples form a distribution than can be used to estimate said probability. We have added following sentence:
TODO: is the sentence below enough? Paul: Please note my change to the below sentence.
\end{reply}

\textit{
\ldots and the probability is computed from a normal approximation of the uncertainty in the cross-validation performance comparison using the mean and standard error of the elpd difference between reference and submodel \citep{Vehtari+etal:2017:practical,paper:projpred,Sivula+etal:2020:loo_uncertainty}.
}

\begin{point}
It is not very exigent in (2) to impose that $\text{elpd}_i-\text{elpd}_\text{best}>0$? Perhaps you should consider other limits similar to those used in Bayes factors (Kass and Raftery, 1995) and not to choose only on solution but to explore other possible solutions in the spirit of Occam’s window
\end{point}

\begin{reply}
The above condition is derived from the original criteria to choose the model size in \citet{paper:projpred} for the use of the projection predictive approach in the minimal subset scenario. In that case, the comparison is between the predictive score of the submodel of size $i$ and the reference model. Here we decided to compare the submodel of size $i$ with the ``best'' size, at the given iteration, due to the natural loss of explanatory power of the remaining covariates as the iterations increase. \\
In general, the condition is expressed as the probability of that event, which is anyhow less exigent than the inequality itself. We don't want to imply that this procedure could not be improved somehow to take, for example, something like Occam's window into account. However, since the projection predictive approach was not the main point of this paper, we cannot reasonably address it here, and leave it for future research. We have added a following sentence to the paper.
TODO: would this be enough? Paul: please note that I changed the sentence below
\end{reply}

@@

\begin{reply}
Thanks for the suggestion. We discuss the computational aspects in Section 2.2. In general, the reference model approach has the additional cost of fitting the reference model before performing selection. However, this reference models is usually available anyway when building up a model via robust workflows \citep{gelman2020bayesian}. Therefore, in these cases there is no additional cost. In any case we believe that the benefits of a more stable and efficient selection overcome the cost of fitting a reference model.
\fede{We added a new table (Table 3) reporting the computational time for the bodyf fat example, showing how the burden is divided between the fit of the reference model and the rest of the selection procedure.}
Paul: why is this still in red?
\end{reply}

\begin{point}
Please add a brief summary of the results you obtained in Section 3 and the main message you infer from these results before moving onto Section 4.
\end{point}

\begin{reply}
This is a good idea. We added a new Section 3.3 which summarises and elaborate the results of Section 3. In particular, we write:

\vspace{0.5\baselineskip}
\textit{
The previous experiments allowed us to study the impact of using reference models in variable selection and to disentangle their influence from that of the actual variable selection method, specifically in the minimal subset selection case.
The simulation study based on artificial data of Section 3.1 shows clear improvements in terms of predictive performance of the selected model and false discovery rate when the selection is based on a reference model, regardless of the actual variable selection method applied. These results are confirmed also in the real word data example with the body fat dataset. The stepwise selection achieves far better selection when coupled with the reference model approach (see Figure 5 and Table 4). However, the projection predictive approach remains the best method in any of the experiments we run and on all the performance indexes we measured. Although we designed a reference model approach for general selection method, the projection predictive approach is a principled and validated way to do the selection. Indeed, the purpose of the former is only for fair comparisons in our study rather than a ready-to-use selection method.
}
\vspace{0.5\baselineskip}
\end{reply}

### 2022-02-16 paper/ref_approach.tex
minor edits

\fede{In general, there is no restriction on the type of model the reference models should be and a sensible reference model does not even need to be Bayesian necessarily.
However, Bayesian methods can help in some of those situations
where MLE procedures struggle. 
It is known that as the number of parameters in the model increases, the MLE
estimator is dominated by shrinkage estimators 
\citep{stein1956inadmissibility, stein1961estimation, parmigiani2009decision, efron2011tweedie}.
The use of a prior in Bayesian inference automatically incorporates 
some kind of shrinkage in the Bayesian estimator under a given loss function \citep[see, e.g.][]{rockova2012hierarchical}. 
For the sake of our study, we rely on simple data structure which can be well described 
by linear regression models. However, more complex data can arise in practice, for example, including hierarchical structures. In these cases, MLE inference tends to become cumbersome, whereas the Bayesian framework provides a natural way to convey uncertainties and make inference through the joint posterior distribution of all parameters.}

@@

\subsection{Reference model's effect and the projection predictive approach}
\fede{The previous experiments allowed us to study the impact of using reference models in variable selection and to disentangle their influence from that of the actual variable selection method, specifically in the minimal subset selection case.
The simulation study based on artificial data of Section 3.1 shows clear improvements in terms of predictive performance of the selected model and false discovery rate when the selection is based on a reference model, regardless of the actual variable selection method applied. These results are confirmed also in the real word data example with the body fat dataset. The stepwise selection achieves far better selection when coupled with the reference model approach (see Figure 5 and Table 4). However, the projection predictive approach remains the best method in any of the experiment we run and on all the performance indexes we measured. Although we designed a reference model approach for general selection method, the projection predictive approach is a principled and validated way to do the selection. Indeed, the purpose of the former is only for fair comparisons in our study rather than a ready-to-use selection method.}

>>>>

\fede{In general, there is no restriction on the type of model the reference models should be, and a sensible reference model does not even need to be Bayesian necessarily.
However, Bayesian methods can help in some of those situations
where MLE procedures struggle. 
It is known that as the number of parameters in the model increases, the MLE
estimator is dominated by shrinkage estimators 
\citep{stein1956inadmissibility, stein1961estimation, parmigiani2009decision, efron2011tweedie}.
The use of a prior in Bayesian inference automatically incorporates 
some kind of shrinkage in the Bayesian estimator under a given loss function \citep[see, e.g.][]{rockova2012hierarchical}. 
For the sake of our study, we rely on simple data structure which can be well described 
by linear regression models. However, more complex data can arise in practice, for example, including hierarchical structures. In these cases, MLE inference tends to become cumbersome, whereas the Bayesian framework provides a natural way to convey uncertainties and make inference through the joint posterior distribution of all parameters.}

@@

\subsection{Reference model's effect and the projection predictive approach}
\fede{The previous experiments allowed us to study the impact of using reference models in variable selection and to disentangle their influence from that of the actual variable selection method, specifically in the minimal subset selection case.
The simulation study based on artificial data of Section 3.1 shows clear improvements in terms of predictive performance of the selected model and false discovery rate when the selection is based on a reference model, regardless of the actual variable selection method applied. These results are confirmed also in the real word data example with the body fat dataset. The stepwise selection achieves far better selection when coupled with the reference model approach (see Figure 5 and Table 4). However, the projection predictive approach remains the best method in any of the experiments we run and on all the performance indexes we measured. Although we designed a reference model approach for general selection method, the projection predictive approach is a principled and validated way to do the selection. Indeed, the purpose of the former is only for fair comparisons in our study rather than a ready-to-use selection method.}
